---
title: "Github Demo"
author: "Bill Wood"
date: "Saturday, May 16, 2015"
output: html_document
---

test entry

# Introduction

**There are two parts to this demo.**

1. Installing packages directly from GitHub
2. Saving code from RStudio with GitHub


## Installing Packages from GitHub

There are a couple of tools you can use to install packages directly from GitHub.

1. devtools (this requires installing Rtools)
2. pacman

### Installing devtools

```{r eval=FALSE}
install.packages("devtools")
library("devtools")
```

You'll be told that you need to install Rtools from the following URL
http://cran.r-project.org/bin/windows/Rtools/

Then run find_rtools() to make sure R knows where to find them

```{r eval=FALSE}
find_rtools()
```
```{r echo=FALSE}
devtools::find_rtools()
```

### Installing a GitHub package from devtools

```{r eval=FALSE}
install_github("hadley/tidyr")
```
```{r echo=FALSE}
devtools::install_github("hadley/tidyr")
```

### Installing pacman

```{r eval=FALSE}
install.packages("pacman")
library("pacman")
```

### Installing a GitHub package from pacman

```{r eval=FALSE}
p_load_gh("trinker/wakefield")
```
```{r echo=FALSE}
pacman::p_load_gh("trinker/wakefield")
```


## Using GitHub from within RStudio

### Setting up GitHub with RStudio

http://www.molecularecologist.com/2013/11/using-github-with-r-and-rstudio/

1. Setup a GitHub account. (A free account allows you to publish public repositories)
2. Download and install Rstudio.
3. Download and install the platform-specific Git client
4. Configure Git with global commands as follows in Git Bash     
  git config –global user.name “your GitHub account name”                                                     
  git config –global user.email “GitHubEmail@something.com”
5. Open Rstudio and set the path to Git executable.    
  Go to Tools > Global Options > Git/SVN and add the path to the git executable

### Configuring a project with GitHub

You can either add git to an existing project or create a project from an existing git repository

We are going to walk through creating a clone from the Rphx Github repository and creating a project in RStudio. There are two ways to do it.

#### 1. Create a project from a local repository

In this method, first you clone the repository to a local directory, then create the project

1. Using the Git Gui, choose Clone Existing Repository  
  + **Source Location**: https://github.com/Rphx/GithubDemo.git  
  + **Target Directory**: wherever you want to create the project.  
  + The Target directory must not exist yet. This will pull the files from the remote repository into the new directory
2. Using RStudio, create a new project from an existing Git repository    
  + In the upper right corner, select New Project...
  + From an Existing Directory...
  + When you create a project from a Git repository it will automatically have Git enabled

#### 2. Create a project directory from a remote repository

1. Using RStudio, select New Project... from the upper right corner
2. Select Version Control
3. Select Git
4. Enter the required information:    
  **Repository URL**: https://github.com/Rphx/GithubDemo.git    
  **Project directory name**:    
  **Create project as a subdirectory of**:    
  Select **Open in new window** if you want to open another instance of RStudio with the new project

#### Working with Git  

Some Basic Git terminology:
* **Clone** - To copy from a parent repository to a new child repository    
* **Add** - Tell Git to start monitoring the file    
* **Commit** - Tell Git to update the local repository with the changes    
* **Push** - Upload changes to the remote repository    
* **Pull** - To download the latest files from the remote repository

#### Working with Git in RStudio

 


https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN

