---
title: "Github Demo"
author: "Bill Wood"
date: "Saturday, May 16, 2015"
output: html_document
---

# Introduction

**There are two parts to this demo.**

1. Installing packages directly from GitHub
2. Saving code from RStudio with GitHub


## Installing Packages from GitHub

There are a couple of tools you can use to install packages directly from GitHub.

1. devtools (this requires installing Rtools)
2. pacman

### Installing devtools

```{r eval=FALSE}
install.packages("devtools")
library("devtools")
```

You'll be told that you need to install Rtools from the following URL
http://cran.r-project.org/bin/windows/Rtools/

Then run find_rtools() to make sure R knows where to find them

```{r eval=FALSE}
find_rtools()
```
```{r echo=FALSE}
devtools::find_rtools()
```

### Installing a GitHub package from devtools

```{r eval=FALSE}
install_github("hadley/tidyr")
```
```{r echo=FALSE}
devtools::install_github("hadley/tidyr")
```

### Installing pacman

```{r eval=FALSE}
install.packages("pacman")
library("pacman")
```

### Installing a GitHub package from pacman

```{r eval=FALSE}
p_load_gh("trinker/wakefield")
```
```{r echo=FALSE}
pacman::p_load_gh("trinker/wakefield")
```


## Using GitHub from within RStudio

http://www.molecularecologist.com/2013/11/using-github-with-r-and-rstudio/

1. Setup a GitHub account.
2. Download and install Rstudio.
3. Download and install the platform-specific version of Git (not GitHub), default options   work well.
4. Configure Git with global commands. I have found this step necessary both times I ran through this process. 

Open up the bash version of Git and type the following:         
  git config –global user.name “your GitHub account name”                                                     
  git config –global user.email “GitHubEmail@something.com”

5. Open Rstudio and set the path to Git executable. Go to Tools > Options > Git/SVN 

https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN
